\documentclass[options]{article}
\begin{document}
\textbf{MUBIRU GRACE\\}
\textbf{REGN.NO. 15/U/7729/PS\\}
\textbf{STUDNT NO.215004794\\}
\textbf{HOW TO BECOME GUILD PRESIDENT   BY BRIBING.}
\section{\textbf{Introduction.}}
A guild president is the representative of students at the university council, he is also a student leader like we have Semboga Roy whose presidence also came in as a surprise. Very many students would love to contest for that post but limited by the high level of competition and the costs incured. Like compaign expances, nomination fee and other costs.
\subsection{Requirements:}
For one to be nominated as guild president has to meet the following requirements:
\subsubsection{Nomination fee.}
One should have fully paid the required nomination fee of two hundred thousand shillings from some universities.
\subsubsection{fully registered student.}
One has to be a fully registered student of Makerere university with a good academic record thus no retake in any possible cases,
and has to be a continuing student.
\section{BRIBING.}
Bribing comes in for those candidates that are less compitent but their love for leadership is aggressive, those candidates can use the following skills of briberly to get the jackport in their favour.
with refference to the currrent guild president MR. Sembuga Roy,  evidence from campus bee shows that during his campaign he used alot of bribing than talking.
\subsection{Bribing the chairman electrol commission.}
the electrol commission is in charge of the univerity's voting and the anouncement of vote results to the university boby. All the power of anouncing the results is held the chairman electrol commission. With success this is the simplest way of becoming a guild president in this corrupt country. if the Chairman is not corrupt then we can try iout other ways. like  carrying out petitions to the courts of law.
\subsection{Bribing the Dean of students.}
In order to win petitions one should have some high profile university leaders in his/ her supprot. like in the case of the current guild president of makerere, he had support from the dean of students.
In case that fails go ahead and bribe the judges.
\subsection{Bribing voters.}
In case one fails to bribe the chairman electrol commission then the contestant should bribe voters. this is a weaker way of fighting for power which personaly i don't recomend. voters can easily be won by how much you spend on them. This can be done in many ways like throwing parties for them, poradge nights etc.
\section{Conclusion}
Its concluded that being a leader depends upon the contestants, if you can't convince them, bribe them.
\end{document}